Parity results

### 2019-08-28 writeUp/parity_results.tex
Started new write up

>>>>

\subsection{Country-level estimates}
I have estimated country-level lifespans for the $n=541$ data points where GPS location was available. The lifespans are plotted in \verb|detinova_lifespan_gambiae_country.pdf|, which determines that Senegal has, on average, the longest lifespan. K-fold CV, however, indicated that these country-level differences were not significant, since a model grouping at the continent level performed better on out-of-sample prediction. This better performance was almost uniformly observed across the countries in the dataset.

\subsection{With or without Reunion}
On inspection of the plots of lifespan against temperature range (see \verb|detinova_gambiae_daynight_range_lifespan_country.pdf|), it looked as if the results may hinge on the data from Reunion. I, hence, repeated the analysis with/without this country. With this country included (see \verb|fit_complex_daynightmax.rds|), the models with linear and quadratic temperature terms fitted the data better. Without Reunion, the linear model fitted the data best but the difference in fit was weaker (compare \verb|detinova_gambiae_daynight_range_lifespan_country.pdf| with \verb|detinova_gambiae_daynight_range_lifespan_noreunion_country.pdf|) and no longer significant at the 5\% level (\verb|fit_complex_daynightmax_noreunion.rds|).
